Coeficientes para la corrección de bias

### 2020-10-29 analysis/chapters/coeficientes.Rmd
Grafico de resumen sin observaciones rechazadas

@@

total <- diag_rad %>% 
  .[, .(bias_tbc = mean(tbc, na.rm = TRUE),
        bias_tbcnob = mean(tbcnob, na.rm = TRUE)), 
    by = .(sensor, channel, exp)] %>% 
  dcast(sensor + channel ~ exp, value.var = "bias_tbc") %>% 
  .[, abs_bias := abs(week2) - abs(week1)] %>% 
  melt(measure.vars = c("week1", "week2"), value.name = "bias_tbc", variable.name = "exp") %>% 
  # .[abs_bias, on = c("sensor", "channel", "exp")] %>% 
  .[n_obs, on = c("sensor", "channel", "exp")]

total %>% 
  .[!(sensor %in% c(multiespectrales, "atms_npp"))] %>% 
 # dcast(sensor + channel + N ~ exp, value.var = "bias_tbc")
  ggplot(aes(channel, sensor)) +
  geom_point(aes(color = abs_bias, size = N)) +
  geom_point(data = ~.x[win == exp], shape = 21, aes(size = N)) +
  # geom_text(aes(label = round(abs_bias, 1)), size = 2) +
  # scale_color_viridis_c(trans = scales::log_trans(), breaks = c(0.1, 1, 10, 100),
  #                       guide = guide_colourbar(barwidth = 7)) +
  scale_color_divergent(trans = symlog_trans(), breaks = c(-1, 0, 1, 10),
                        guide = guide_colourbar(barwidth = 7)) +
  facet_wrap(~exp, labeller = labeller(exp = c("week1" = "pre-RAD1", "week2" = "pre-RAD2"))) +
  labs(subtitle = "all obs",
       color = "Bias\ndifference",
       size = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

>>>>

satinfo <- fread(here("analysis", "data", "raw_data", "satinfo.txt")) %>% 
  setnames(c("!sensor/instr/sat", "chan"), c("sensor", "channel"))

@@

total <- diag_rad %>% 
  .[, .(bias_tbc = mean(tbc, na.rm = TRUE),
        bias_tbcnob = mean(tbcnob, na.rm = TRUE)), 
    by = .(sensor, channel, exp)] %>% 
  dcast(sensor + channel ~ exp, value.var = "bias_tbc") %>% 
  .[, abs_bias := abs(week2) - abs(week1)] %>% 
  melt(measure.vars = c("week1", "week2"), value.name = "bias_tbc", variable.name = "exp") %>% 
  # .[abs_bias, on = c("sensor", "channel", "exp")] %>% 
  .[n_obs, on = c("sensor", "channel", "exp")] %>% 
  satinfo[., on = c("sensor", "channel")]

total[iuse == 1] %>% 
  .[!(sensor %in% c(multiespectrales, "atms_npp"))] %>% 
 # dcast(sensor + channel + N ~ exp, value.var = "bias_tbc")
  ggplot(aes(channel, sensor)) +
  geom_point(aes(color = abs_bias, size = N)) +
  geom_point(data = ~.x[win == exp], shape = 21, aes(size = N)) +
  # geom_text(aes(label = round(abs_bias, 1)), size = 2) +
  # scale_color_viridis_c(trans = scales::log_trans(), breaks = c(0.1, 1, 10, 100),
  #                       guide = guide_colourbar(barwidth = 7)) +
  scale_color_divergent(trans = symlog_trans(), breaks = c(-1, 0, 1, 10),
                        guide = guide_colourbar(barwidth = 7)) +
  facet_wrap(~exp, labeller = labeller(exp = c("week1" = "pre-RAD1", "week2" = "pre-RAD2"))) +
  labs(subtitle = "all obs",
       color = "Bias\ndifference",
       size = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
